% =====================================================================
% JMIR Research Protocols requires a structured abstract:
% Background / Objective / Methods / Results / Conclusions
% plus the International Registered Report Identifier (IRRID) line at the end.
% Length: typically 300--400 words.
% =====================================================================

\begin{abstract}
\noindent \singlespacing

\noindent \textbf{Background:} The objective assessment of cognitive performance during ordinary teaching is a longstanding methodological gap in educational research. Conventional instruments --- summative tests, retrospective self-report, lesson-end ratings --- operate at a temporal grain orders of magnitude coarser than the underlying construct and carry well-documented subjective biases. Multimodal passive sensing offers continuous, ecologically valid monitoring through ambient, physiological, neurophysiological and behavioural signals, but the constituent technologies have so far matured in disconnected silos rather than as integrated longitudinal classroom systems.

\noindent \textbf{Objective:} This protocol describes an observational, prospective, longitudinal study in two groups of Spanish compulsory secondary education students (3rd and 4th of ESO, ages 14--16) that integrates, in one ecologically valid four-month deployment, a CEIS-UCLM-approved multimodal passive sensing platform with a 5-minute teacher-annotated cognitive-performance label and a Psychomotor Vigilance Task (PVT) external anchor. The primary objective is to characterise the platform's measurement properties before any inferential modelling and to deposit the resulting derived dataset under restricted access for the multimodal learning analytics community.

\noindent \textbf{Methods:} Four passive streams are recorded in synchrony: (i)~a UCLM ad-hoc ambient platform (temperature, relative humidity, CO\textsubscript{2}, PM2.5, PM10, illuminance, sound pressure level at 15 Hz; no audio waveform); (ii)~EmotiBit physiological wristbands (heart rate, heart-rate variability, electrodermal activity, peripheral skin temperature and tri-axial accelerometry; six units rotating weekly with sex-balanced allocation); (iii)~a Bitbrain Versatile 32-channel semi-dry electroencephalography system at 256~Hz on one stratified-sampled participant per week; and (iv)~overhead Reolink 4K dual-lens video (180\textdegree) processed exclusively for body-pose features, with the raw footage deleted within 72~hours of feature extraction under a verifiable governance log. The cognitive-performance label is a binary teacher annotation per 5-minute window. External validation comprises the PVT administered monthly before and after instrumented sessions and an end-of-session 0--10 global rating. The study is observational; no educational intervention is delivered. Recruitment is class-complete in the instrumented reference classroom with a comparison group of the same school year. \textcolor{blue}{The principal technical contribution underpinning this protocol is a dual-plane software architecture using MQTT with Quality of Service 2 (QoS 2) and source-based Network Time Protocol (NTP) timestamping. The protocol targets sub-100 ms inter-modality alignment; bench-test validation of the timestamping mechanism yields an end-to-end synchronisation error below 15 ms, overcoming the synchronisation limitations of traditional tethered laboratory setups.}

\noindent \textbf{Results:} The study was approved in principle by the Ethics in Social Research Committee of the Universidad de Castilla-La Mancha (CEIS-UCLM, reference \texttt{[PENDING]}). Recruitment is expected to begin once the consent-and-assent campaign closes; data collection is anticipated to run for four months thereafter. We report the planned analytical framework, the per-modality validation protocols (synchronisation latency, physiological signal quality, EEG signal quality, body-pose detection performance, environmental sensor responsivity), the statistical-analysis plan and the residual risks (single-annotator labelling, single-school deployment, special-category data of minors) that the team commits to characterise quantitatively in subsequent compendium articles.

\noindent \textbf{Conclusions:} The protocol describes a CEIS-UCLM-approved measurement infrastructure that will support subsequent predictive analyses in the doctoral compendium. The methodological contribution is the joint operationalisation, in a single ecologically valid longitudinal deployment, of four passive multimodal streams, a teacher-anchored 5-minute label and a PVT external benchmark --- under European data-protection guarantees for minors, with privacy-preserving on-server processing and a tiered data-release regime.

\end{abstract}
