% =====================================================================
% JMIR Research Protocols — Acknowledgements, Funding, CRediT,
% Conflicts of Interest, Abbreviations
% =====================================================================

\phantomsection
\section*{Acknowledgements}\label{sec:ack}

This work is part of the doctoral programme \emph{Investigación en Humanidades, Artes y Educación} of the Universidad de Castilla-La Mancha (UCLM). The UCLM ad-hoc ambient sensing platform was developed within the UCLM teaching-innovation project ``Aulas inteligentes para la mejora de la atención del estudiantado mediante algoritmos de Inteligencia Artificial integrados con visión artificial y tecnologías embebidas.'' The authors thank \texttt{[SCHOOL NAME --- pending CEIS approval and consent campaign]} and the participating students, families and teaching staff. The theoretical and methodological foundation of this protocol builds directly upon the team's prior scoping review of the multimodal classroom sensing literature. No generative artificial intelligence tools were used in the writing of this manuscript.

\phantomsection
\section*{Funding}\label{sec:funding}

This research derives findings from the parent national project PID2022-137397NB-I00 (\emph{Impacto de un programa de actividad física en alumnado con altas capacidades en Educación Primaria para mejorar el bienestar cognitivo y socioemocional}), funded by the Spanish Ministry of Science and Innovation (MICINN). The present protocol is observational and is not part of the parent project's intervention arm at the primary-education level. The opinions, findings, conclusions and recommendations expressed in this article are those of the authors and do not necessarily reflect the views of the funding bodies.

\phantomsection
\section*{Authors' Contributions}\label{sec:credit}

Following the CRediT taxonomy: \textbf{José Enrique Herrero Albiar} (doctoral candidate): Conceptualization; Methodology; Software; Investigation; Data Curation; Writing --- Original Draft. \textbf{Eloy García-Pérez}: Methodology; Resources; Validation; Writing --- Review \& Editing. \textbf{Javier Martínez-López}: Software (hardware design and firmware of the UCLM ad-hoc ambient platform); Validation; Writing --- Review \& Editing. \textbf{Alejandro L. Borja}: Methodology; Validation; Writing --- Review \& Editing. \textbf{Roberto Sánchez-Reolid}: Conceptualization; Methodology; Software (institutional-server pipeline; time-synchronisation; real-time dashboard); Validation; Writing --- Review \& Editing. \textbf{Juan Carlos Pastor Vicedo} (corresponding author and thesis director): Conceptualization; Methodology; Supervision; Project administration; Funding acquisition; Writing --- Review \& Editing. Enquiries about data governance and ethics should be directed to the corresponding author with copy to the UCLM Data Protection Officer.

\phantomsection
\section*{Conflicts of Interest}\label{sec:competing-interests}

The authors declare that they have no known competing financial interests or personal relationships that could have appeared to influence the work reported in this protocol.

\phantomsection
\section*{Abbreviations}

\begin{description}[leftmargin=*, itemsep=1pt]
\item[BOSS] Behavioral Observation of Students in Schools
\item[CEIS] Ethics in Social Research Committee (Comité de Ética en Investigación Social)
\item[EDA] Electrodermal activity
\item[EEG] Electroencephalography
\item[ESO] Compulsory Secondary Education (Educación Secundaria Obligatoria)
\item[GDPR] General Data Protection Regulation
\item[HR] Heart rate
\item[HRV] Heart rate variability
\item[ICA] Independent component analysis
\item[IEQ] Indoor environmental quality
\item[IMU] Inertial measurement unit
\item[IRRID] International Registered Report Identifier
\item[LOPDGDD] Spanish Organic Law on Data Protection and Digital Rights
\item[ML] Machine learning
\item[MMLA] Multimodal learning analytics
\item[MQTT] Message Queuing Telemetry Transport
\item[NTP] Network Time Protocol
\item[PPG] Photoplethysmography
\item[PVT] Psychomotor Vigilance Task
\item[QoS] Quality of Service
\item[SPL] Sound pressure level
\item[UCLM] Universidad de Castilla-La Mancha
\item[VOC] Volatile organic compounds

\vspace{0.5em}
\noindent BOSS category abbreviations: AET (Active Engaged Time), PET (Passive Engaged Time), OFT-P (Off-Task Passive), OFT-M (Off-Task Motor), OFT-V (Off-Task Verbal).
\end{description}

\endinput
