% =====================================================================
% JMIR Research Protocols — Acknowledgements, Authors' Contributions
% (CRediT) and Conflicts of Interest. Co-author confirmation pending
% before submission.
% =====================================================================

\phantomsection
\section*{Acknowledgements}\label{sec:ack}

This work is part of the doctoral programme \emph{Investigación en Humanidades, Artes y Educación} of the Universidad de Castilla-La Mancha (UCLM). The research derives findings from the parent national project PID2022-137397NB-I00 (\emph{Impacto de un programa de actividad física en alumnado con altas capacidades en Educación Primaria para mejorar el bienestar cognitivo y socioemocional}); the present protocol is observational and is not part of the parent project's intervention arm at the primary-education level. The UCLM ad-hoc ambient sensing platform was developed within the UCLM teaching-innovation project ``Aulas inteligentes para la mejora de la atención del estudiantado mediante algoritmos de Inteligencia Artificial integrados con visión artificial y tecnologías embebidas.'' The authors thank \texttt{[SCHOOL NAME --- pending CEIS approval and consent campaign]} and the participating students, families and teaching staff. The theoretical and methodological foundation of this protocol builds directly upon the team’s prior scoping review (Herrero Albiar et al., 2026, under review). The opinions, findings, conclusions and recommendations expressed in this article are those of the authors and do not necessarily reflect the views of the funding bodies.

\phantomsection
\section*{Authors' Contributions}\label{sec:credit}

Following the CRediT taxonomy: \textbf{José Enrique Herrero Albiar} (doctoral candidate): Conceptualization; Methodology; Software; Investigation; Data Curation; Writing --- Original Draft. \textbf{Eloy García-Pérez}: Methodology; Resources; Validation; Writing --- Review \& Editing. \textbf{Javier Martínez-López}: Software (hardware design and firmware of the UCLM ad-hoc ambient platform); Validation; Writing --- Review \& Editing. \textbf{Alejandro L. Borja}: Methodology; Validation; Writing --- Review \& Editing. \textbf{Roberto Sánchez-Reolid}: Conceptualization; Methodology; Software (institutional-server pipeline; time-synchronisation; real-time dashboard); Validation; Writing --- Review \& Editing. \textbf{Juan Carlos Pastor Vicedo} (corresponding author and thesis director): Conceptualization; Methodology; Supervision; Project administration; Funding acquisition; Writing --- Review \& Editing. Enquiries about data governance and ethics should be directed to the corresponding author with copy to the UCLM Data Protection Officer.

\phantomsection
\section*{Conflicts of Interest}\label{sec:competing-interests}

The authors declare that they have no known competing financial interests or personal relationships that could have appeared to influence the work reported in this protocol.
